### 2014-04-22 tex/main-body-text.tex
Added some results and a figure under images in a Figures-Pat folder

\subsection*{{\sc flock} analysis of coasta California steelhead} 
{\sc flock} was run four times using the default setting for all run parameters \textit{(initial partition = random, number of iterations = 20, number of runs = 50, LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of \textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were produced. 
Run times were relatively short. The four groups of runs for the default settings averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no plateaus were observed in any of the four groups for a \textit{k} greater than two, the plateau record varied greatly among each group for \textit{k}=2 (plateau sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). Using the plateau analysis procedure suggested by \citet{Duc&Tur2012} either \textit{k}=2 is the lower bound estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite different conclusions, the allocation of individuals for the 'best run' from each group differed by a only a single individual. When \textit{k}=2, {\sc flock} identifies a boundary in the Russian Gulch area clustering individuals into northern and southern groups. With increased \textit{k} {\sc flock} splits individuals collected from the same stream between clusters. Increasing the number of iterations from 20 to 100 did not yield an increase in plateau length.

\section*{Conclusions}
The partition space over which {\sc flock} evaluates how individuals are clustered greatly increases with both the number of individuals and the number of clusters into which they can be partitioned. The total partition space for any given k can be defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the second kind. The results of {\sc flock} depend primarily on the initial partition of individuals. It is not surprising that with 2,596 individuals we could have drastically different plateau sequences with just two clusters.

>>>>

\subsection*{{\sc flock} analysis of coasta California steelhead} 
{\sc flock} was run four times using the default setting for all run parameters \textit{(initial partition = random, number of iterations = 20, number of runs = 50, LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of \textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were produced. 
Run times were relatively short. The four groups of runs for the default settings averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no plateaus were observed in any of the four groups for a \textit{k} greater than two, the plateau record varied greatly among each group for \textit{k}=2 (plateau sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to two different conclusions for the plateau sequences observed: \textit{k}=2 is the lower bound estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite different conclusions, the allocation of individuals for the 'best run' from each group differed by a only a single individual. When \textit{k}=2, {\sc flock} identifies a boundary in the Russian Gulch area clustering individuals into northern and southern groups (Fig. 1).

\begin{figure}
    \includegraphics[width=8.0in]{FLOCK_OneSampDefault.tif}
    \caption{Assignment to reference population (from \textit{k} = 2-6) plots created in the program {\sc flock}. Each horizontal plot represents the 'best run' from a series where individuals are reallocated into \textit{k} clusters. Within each plot the normalized individual likelihood for each reference population is represented by a colored vertical bar. Major geographic boundaries that were attributed to genetic structure in \citet{Garzaetal_norcal} are indicated with black vertical lines. Results from the 'best runs' showed similar geographic differentiation to \citet{Garzaetal_norcal} analysis. The plateau analysis developed by \citet{Duc&Tur2012} indicate that either an undecided structure or that \textit{k}=2 is the lower bound estimate.}
    \label{Fig.1}
\end{figure}

With increased \textit{k} {\sc flock} continues to splits individuals approximately based on geographical boundaries identified by \citet{Garzaetal_norcal} using {\sc structure}. Once \textit{k} = 6 is reached no new regions are identified.

To investigate the ability of the arrangement of individuals within the reference populations to move around the partition space we varied the number of iterations that each run goes through to find the 'optimal' allocation of individuals. Unfortuantely only the reallocation matrix for the 'best run' is given as output. Increasing the number of iterations did not affect the overall inference of \textit{k}. It was observed that often during the last iterations individuals would alternate between reference groups during subsequent iterations. Increasing the log likelihood difference threshold for reallocation to 0.18 (there needs to be at least a 1.5 times higher likelihood to reallocate the individual) minimized this, but did not affect the inference of \textit{k} (lower bound estimate of \textit{k} = 2).

\section*{Conclusions}
The partition space over which {\sc flock} evaluates how individuals are clustered greatly increases with both the number of individuals and the number of clusters into which they can be partitioned. The total partition space for any given k can be defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the second kind. The results of {\sc flock} depend primarily on the initial partition of individuals. It is not surprising that with 2,596 individuals we could have drastically different plateau sequences with just two clusters. It is difficult to access how well the reallocation process moves the cluster of individuals within the partition space due to the fact that the reallocation matrix from only the 'best-run' is reported.
